---
title: "RWorksheet#5_group(Leysa,Calambro)"
author: "Camilo Leysa"
date: "2024-11-11"
output: pdf_document
---


Loading needed libraries:
```{r}
library(rvest)
library(polite)
library(dplyr)
library(httr)
library(stringr)
library(ggplot2)
```

```{r}
polite::use_manners(save_as = "polite_scrape_tvshows.R")
url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250" 
session <- bow(url, user_agent = "Educational")
session
```

1. 

Getting the TV Show title.
```{r}
#Title
title_lists <- scrape(session) %>% html_nodes("h3.ipc-title__text") %>% html_text(trim = TRUE)
#filter unwanted
title_lists <- title_lists[!grepl("Recently viewed", title_lists)]
title_lists
```

List of top 50 TV Shows
```{r}
class(title_lists)
title_List <- as.data.frame(title_lists[2:51])
title_List
```

Seperating the rank number and the TV Show title.
```{r}
colnames(title_List) <- "ranks"
split_df <- strsplit(as.character(title_List$ranks),".",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))
split_df <- split_df[-c(3:4)] 
colnames(split_df) <- c("Ranks","Title") 
str(split_df)
```

The Rank and the Title of the TV Shows
```{r}
class(split_df)
split_df
```

Top 50 TV Show Rating
```{r}
rating <- scrape(session) %>% html_nodes("span.ipc-rating-star--rating") %>% html_text
tv_rating <- as.data.frame(rating [1:50])
tv_rating
```
Number of People who Voted
```{r}
tv_votes <- scrape(session) %>% html_nodes("span.ipc-rating-star--voteCount") %>% html_text
total_tv_votes <- as.data.frame(tv_votes[1:50])
total_tv_votes
```
Number of Episodes of each TV Shows
```{r}
episodes <- scrape(session) %>% html_nodes("span.sc-6ade9358-7.exckou.cli-title-metadata-item") %>% html_text
cl_episodes <- gsub("\\D", "", episodes)
cleaned_ep <- str_extract(episodes, "\\d+(?=\\s*eps)")
cleaned_ep <- as.numeric(cleaned_ep)
cleaned_ep <- cleaned_ep[!is.na(cleaned_ep)]
cleaned_episodes <- as.data.frame(cleaned_ep[1:25])
cleaned_episodes
```
Year of TV Shows released
```{r}
tv_years <- scrape(session) %>% html_nodes("span.sc-6ade9358-7.exckou.cli-title-metadata-item") %>% html_text
clyear <- gsub(".*?(\\d{4}(-\\d{4})?).*", "\\1", tv_years)
yeartv <- str_extract(tv_years, "\\b\\d{4}(-\\d{4})?\\b")
yeartv <- as.numeric(yeartv)
yeartv <- yeartv[!is.na(yeartv)]
tv_year_of_air <- as.data.frame(yeartv[1:50])
tv_year_of_air
```

Number of User Reviews
```{r}
review <- scrape(session) %>% html_nodes("ul.ipc-inline-list.sc-b782214c-0.bllRjU.baseAlt") %>% html_text
reviews <- as.data.frame(review[1:50])
reviews
#tried several links but still getting NA's.
```
Getting the number of Critic Reviews
```{r}
critic <- scrape(session) %>% html_nodes("ul.ipc-inline-list.sc-b782214c-0.bllRjU.baseAlt") %>% html_text
critic_rev <- as.data.frame(critic [1:50])
critic_rev
#tried several links but still getting NA's.
```

Getting the popularity Review
```{r}
popularity_review <- scrape(session) %>% html_nodes("div.hero-rating-bar__popularity__down") %>% html_text
pop <- as.data.frame(popularity_review [1:50])
pop
#tried several links but still getting NA's.
```





Data frame of TV Shows
```{r}
final_data <- cbind(split_df,tv_rating,total_tv_votes,cleaned_episodes,tv_year_of_air,reviews,critic_rev,pop)
colnames(final_data) <- c("Ranks", "TV Show Title", "Rating", "Number of People Voted", "Number of Episodes", "Year Released", "User Reviews", "Critic Reviews", "Popularity Review")
final_data
write.csv(final_data, "Top_50_tvshows.csv", row.names = FALSE)
```

2. 5 TV Shows chosen for user reviews.
```{r}
top_5 <- scrape(session) %>% html_nodes("h3.ipc-title__text") %>% html_text(trim = TRUE)
tv_top5 <- as.data.frame(list(Rank_Title = top_5[2:6]), stringsAsFactors = FALSE)
split_list <- strsplit(as.character(tv_top5$Rank_Title), "\\.", fixed = FALSE)
split_Df <- data.frame(do.call(rbind, lapply(split_list, function(x) {
  if(length(x) == 2) {
    return(x)
  } else {
    return(c(x[1], NA))
  }
})), stringsAsFactors = FALSE)[-c(3:4)] 
colnames(split_Df) <- c("Ranks", "Title") 
str(split_Df)
split_Df
```

Getting the reviewer's name
```{r}
urev <- scrape(session) %>% html_nodes("ul.ipc-inline-list.ipc-inline-list--show-dividers.ipc-inline-list--inline.base") %>% html_text
userev <- as.data.frame(urev)
userev
```

Date of Review of the Person
```{r}
revdate <- scrape(session) %>% html_nodes("li.ipc-inline-list__item review-date") %>% html_text
datereview <- as.data.frame(revdate)
datereview
```


User rating
```{r}
user_rate <- scrape(session) %>% html_nodes("span.ipc-rating-star--rating") %>% html_text
tv_rating <- as.data.frame(rating [1:20])
tv_rating
```




3. Graph of each TV show releases each year
```{r}
str(final_data$`Year Released`)
final_data$`Year Released` <- as.numeric(as.character(final_data$`Year Released`))
fdata <- final_data %>% filter(!is.na(`Year Released`))
tv_shows_by_year <- final_data %>%
  group_by(`Year Released`) %>%
  summarise(num_shows = n()) %>%
  arrange(`Year Released`)

# Create a time series plot
ggplot(tv_shows_by_year, aes(x = `Year Released`, y = num_shows)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(title = "Number of TV Shows Released by Year",
       x = "Year",
       y = "Number of Shows") +
  theme_minimal()
```














